Structural controllability of ecological networks

### 2018-06-19 paper/supp-info.Rmd
Alternative title
Figures were on top of titles

---
title: "Ecological network control"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r fig-input-graph, fig.height=fig_input_graph$height, fig.width=fig_input_graph$width,fig.cap = "Input graph. Two nodes $x_i$ and $x_j$ are said to be control adjacent if there is a node $x_k$ connecting $x_i$ and $x_j$ with an unmatched link $x_k-x_i$ and a matched link $x_k-x_j$. For example, in the top panel, $a_1$ is control adjacent to $a_2$ (via $p_2$), $p_1$ is control adjacent to $p_3$ (via $a_1$) and $p_2$ has no control adjacent nodes. As $a_1$ and $p_2$ belong to the minimum driver node set under the control configuration found with the maximum matching shown, then every node in the same component as these two nodes is also a possible driver node. By combining the nodes from the components with minimum driver node sets is possible to enumerate the different control configurations. For example the network in the top panel has two possible minimum driver node sets $[p_2, a_1]$ and $[p_2, a_2]$ (Figure \\@ref(M-fig:fig-control-configuration)). The network in the middle panel has three minimum driver node sets $[x_1, x_2]$, $[x_1, x_3]$, and $[x_1, x_4]$. Finally the network in the bottom pannel has only one $[x_1]$."}
replayPlot(fig_input_graph$plot)
```

@@

```{r fig-bidirectional, fig.height=fig_bidirectional$height, fig.width=fig_bidirectional$width,fig.cap = "In order to calculate the controllability metrics for a network with reciprocal links (left), we first decompose the network into several versions that contain no reciprocal links (right). As each of these networks represents a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks."}
replayPlot(fig_bidirectional$plot)
```

>>>>

---
title: "Structural controllability of ecological networks"
subtitle: "Supplementary Information"
author: "Fernando Cagua, Kate L. Wootton, Daniel B. Stouffer"
classoption: a4paper
csl: journal-of-ecology.csl
documentclass: artikel1
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{xr}
  - \externaldocument[M-]{manuscript}
  - \usepackage{multirow}
bibliography: phd-bibliography/network-control.bib
---

@@

```{r fig-input-graph, fig.height=fig_input_graph$height, fig.width=fig_input_graph$width,fig.cap = "Input graph. Two nodes $x_i$ and $x_j$ are said to be control adjacent if there is a node $x_k$ connecting $x_i$ and $x_j$ with an unmatched link $x_k-x_i$ and a matched link $x_k-x_j$. For example, in the top panel, $a_1$ is control adjacent to $a_2$ (via $p_2$), $p_1$ is control adjacent to $p_3$ (via $a_1$) and $p_2$ has no control adjacent nodes. As $a_1$ and $p_2$ belong to the minimum driver node set under the control configuration found with the maximum matching shown, then every node in the same component as these two nodes is also a possible driver node. By combining the nodes from the components with minimum driver node sets is possible to enumerate the different control configurations. For example the network in the top panel has two possible minimum driver node sets $[p_2, a_1]$ and $[p_2, a_2]$ (Figure \\@ref(M-fig:fig-control-configuration)). The network in the middle panel has three minimum driver node sets $[x_1, x_2]$, $[x_1, x_3]$, and $[x_1, x_4]$. Finally the network in the bottom pannel has only one $[x_1]$.", fig.pos="p"}
replayPlot(fig_input_graph$plot)
```

@@

```{r fig-bidirectional, fig.height=fig_bidirectional$height, fig.width=fig_bidirectional$width,fig.cap = "In order to calculate the controllability metrics for a network with reciprocal links (left), we first decompose the network into several versions that contain no reciprocal links (right). As each of these networks represents a different equiprobable scenario, the controllability metrics for the network with reciprocal links are the unweighted mean of these metrics across the non-reciprocal networks.", fig.pos="p"}
replayPlot(fig_bidirectional$plot)
```
